---
title: "lgbtq_movies"
author: "Vandrade"
date: "2024-06-25"
output: html_document
---

```{r, warning= FALSE}

library(tidyverse)
library(tidytuesdayR)
library(ggforce)
library(ggtext)
library(glue)

tuesdata <- tt_load('2024-06-25')

df <- tuesdata$lgbtq_movies

```

c('#ff0000','#ff7400','#fff400', '#00ff04', '#00ecff')

```{r}

pride <- df |> 
  arrange(release_date) |> 
  mutate(release_year = lubridate::year(release_date),
         id = as.factor(id)) |> 
  rename(p_title = title)

```

```{r}

pride |> 
  group_by(release_year) |> 
  summarise(n = n(),
            adult = sum(adult == TRUE),
            videos = sum(video == TRUE),
            vote_average = mean(vote_average)) |>
  mutate(rep_adult = adult/n) |> 
  arrange(desc(release_year)) |> 
  ggplot(aes(x = release_year, y = n, color = NULL, fill = n)) +
  geom_col() + 
  theme_minimal() +
  labs(x = 'Ano de Lançamento',
       y = NULL) + 
  scale_fill_gradientn(colours = c('#00ecff','#00ff04','#fff400', '#ff7400', '#ff0000')) 


```

```{r}

pride |> 
  mutate(p_title = fct_reorder(p_title, popularity)) |> 
  filter(popularity > 35) |> 
  ggplot(aes(x = p_title, y = popularity, color = NULL, fill = popularity)) +
  geom_col() +
  coord_flip() +
  scale_fill_gradientn(colours = c('#00ecff','#00ff04','#fff400', '#ff7400', '#ff0000')) + 
  theme_minimal() + 
  labs(y = 'Popularity',
       x = NULL)

pride |> 
  mutate(p_title = fct_reorder(p_title, popularity)) |> 
  filter(popularity > 35) |> 
  ggplot(aes(x = p_title, y = log(popularity), color = NULL, fill = log(popularity))) +
  geom_col() +
  coord_flip() +
  scale_fill_gradientn(colours = c('#00ecff','#00ff04','#fff400', '#ff7400', '#ff0000')) +
  theme_minimal() + 
  labs(y = 'Popularity',
       x = NULL)  

```

```{r plot, fig.width = 10, fig.height = 9.2}

pride |> 
  filter(popularity > 1,
         vote_count > 500) |> 
  mutate(id = fct_reorder(id, release_year)) |> 
  ggplot(aes(x = id, y = vote_average, color = release_year, fill = release_year)) +
  geom_link(aes(x = id, xend = id, y = 0 ,yend = vote_average, 
                           alpha = vote_average), n = 300, size = 1) +
  coord_polar(theta = "y", start = 3*pi/2, clip = "off") + 
  geom_point(aes(y = 0), shape = 17, size = .3) + 
  geom_point(aes(y = vote_average + .04, size = log(popularity))) + 
  geom_text(aes(y = 0, label = "|"), family = "Changa", fontface = "bold", size = 4, vjust = 1) + 
  ylim(0, 20)




```


```{r}

pride |>  
  filter(popularity > 10, vote_count > 250) |> 
  arrange(desc(popularity))
    
             
pride |> 
  filter(popularity > 1, vote_count > 200) |> 
  filter(popularity > 10,
         release_year > 1970) |> 
  group_by(release_year) |> 
  summarise(n = n(),
            adult = sum(adult == TRUE),
            videos = sum(video == TRUE),
            vote_average = mean(vote_average)) |>
  mutate(rep_adult = adult/n) |> 
  arrange(desc(release_year)) |> 
  ggplot(aes(x = release_year, y = n, color = NULL, fill = release_year)) +
  geom_col() + 
  theme_minimal() +
  labs(x = 'Ano de Lançamento',
       y = NULL) + 
  scale_fill_gradientn(colours = c('#00ecff','#00ff04','#fff400', '#ff7400', '#ff0000')) + 
  xlim(1970, 2022)

```



```{r plot, fig.width = 25, fig.height = 23.63}



pride_graf <- pride |> 
  filter(vote_count > 200,
         popularity > 1) |> 
  mutate(id = fct_reorder(id, desc(release_date)),
         release_id = row_number(id))


df_labs <- pride_graf |> 
  filter(release_year %in% c(1943, 1990, 2000, 2010, 2015, 2018, 2021)) |> 
  group_by(release_year) |> 
  summarise(release_year = min(release_year),
            id = first(id),
            release_id = first(release_id))


skeleton <- pride_graf|>
  ggplot(aes(x = release_id, y = log(popularity), color = -release_year, fill = -release_year)) +
  geom_link(aes(x = release_id, xend = release_id, y = 0 , yend = log(popularity), 
                           alpha = log(popularity)), n = 300, size = 1) +
  coord_polar(theta = "y", start = 3*pi/2, clip = "off") + 
  geom_point(aes(y = 0), shape = 17, size = 2) + 
  geom_point(aes(y = log(popularity), size = vote_average)) +
  geom_text(data = df_labs, aes(y = 0, label = "|"), family = "Changa", fontface = "bold", size = 5, vjust = 1) + 
  scale_color_gradientn(colours = c('#00ecff','#00ff04','#fff400', '#ff7400', '#ff0000')) +
  geom_richtext(data = df_labs, aes(y = 0, label = release_year), size = 11, family = "Oswald", fontface = "bold",
                fill = NA, label.color = NA, vjust = 1.5) + 
  # ylim(0, 6.5) + 
  # xlim(-30, 239) + 
  theme_void() + 
  theme(legend.position = 'none',
        plot.background = element_rect(fill = "white")) + 
  labs(x = NULL,
       y = NULL) + 
  geom_textbox(data = tibble(release_id = 239, popularity = 6, label = "<b style='font-size:38pt;'>Most Popular LGBTQ+ Movies of All Time</b><br><br>", release_year = 1943), aes(x = release_id, y = popularity, label = label),
      size = 8,
      family = "Oswald",
      color = "black",
      lineheight = 1.3,
      width = unit(6.2, "inch"),
      hjust = .2,
      vjust = -.8,
      fill = NA,
      box.colour = NA) + 
  annotate("text", x = 239, y = 4.7, label = "Visualization by Vicente Andrade • Data by TidyRainbow from TMDB • Curated by Cara Cuiule", family = "Oswald", size = 5.6, color = "grey50", hjust = .68) +
    scale_x_continuous(limits = c(-40,239)) +
    scale_y_continuous(limits = c(0, 6.5)) 
  

skeleton



```


```{r}

pride_graf |> 
  group_by(release_year) |> 
  summarise(n = n(),
            adult = sum(adult == TRUE),
            videos = sum(video == TRUE),
            vote_average = mean(vote_average)) |>
  mutate(rep_adult = adult/n) |> 
  arrange(desc(release_year)) |> 
  ggplot(aes(x = release_year, y = n, color = NULL, fill = release_year)) +
  geom_col() + 
  theme_minimal() +
  labs(x = 'Ano de Lançamento',
       y = NULL) + 
  scale_fill_gradientn(colours = c('#00ecff','#00ff04','#fff400', '#ff7400', '#ff0000')) + 
  xlim(1970, 2022)

pride_graf |> 
  mutate(p_title = fct_reorder(p_title, popularity)) |> 
  slice_max(order_by = popularity, n = 12) |> 
  ggplot(aes(x = p_title, y = log(popularity), color = NULL, fill = -release_year)) +
  geom_col() +
  coord_flip() +
  scale_fill_gradientn(colours = c('#00ecff','#00ff04','#fff400', '#ff7400', '#ff0000')) +
  theme_minimal() + 
  labs(y = 'Popularity',
       x = NULL) 
  

```

```{r plot, fig.width = 25, fig.height = 23.63}

df_text <- pride_graf |>
  arrange(desc(popularity)) |> 
  slice(c(1:12, 133)) |> 
  mutate(label = glue::glue("<b style='font-size:25pt;'>{p_title}</b> <span style='font-size:20pt;'>({release_year})</span><br><span style='color:#909090; font-size:18pt;'> Average Grade {vote_average} </span>"),
         vjust = c(1,1,1,1,1,.7,1,1,1,1,1,1,0),
         hjust = c(0,0,-2,0,0,0,0,0,0,0,0,0,2)) 
  
skeleton + 
  geom_richtext(data = df_text, aes(label = label, vjust = vjust, hjust = hjust), size = 3.2, family = "Oswald", hjust = .5, lineheight = 1.2, fill = NA, label.color = NA)



```



df_text <-
  df_missions %>% 
  arrange(-hours) %>% 
  slice(c(1:11, 29)) %>% 
  mutate(
    first_name = str_remove(name, ".*, "),
    last_name = str_remove(name, "(?<=),.*"),
    name_short = glue::glue("{str_sub(first_name, 0, 1)}. {last_name}"),
    era = glue::glue("'{str_sub(abs(year), 3, 4)}–'{str_sub(max_year, 3, 4)}"),
    label = glue::glue("<b style='font-size:13pt;'>{name_short}</b>  <span style='font-size:10pt;'>({era})</span><br><span style='color:#909090;'>{format(floor(hours), big.mark = ',')} hours ~ {round(hours / 8760, 1)} years</span>"),
    vjust = c(-.55, -.55, -.55, -.55, -.55, 1.55, .55, -.55, -.4, 1.55, 1.55, 1.55)
  ) %>% 
  ungroup() %>% 
  mutate(
    hours = case_when(
      last_name == "Yurchikhin" ~ hours + 650,
      last_name == "Borisenko" ~ hours + 220,
      last_name == "Kaleri" ~ hours + 100,
      last_name == "Padalka" ~ hours - 500,
      TRUE ~ hours
    ),
    id = case_when(
      last_name == "Kaleri" ~ id + 10L,
      last_name == "Borisenko" ~ id - 18L,
      last_name == "Padalka" ~ id - 60L,
      TRUE ~ id
    )
  )





























